Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-07 paper.tex
figure change

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
complicated by the fact that the programs are unobserved,
and so we must solve a difficult search problem to find any programs at all. To make
search tractable we learn a bottom-up \emph{recognition
  model} alongside the top-down generative model
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs.  The neural network $q$ implements an amortized
inference/compiled inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model by speeding up the search for programs.

@@

We take the intuitive strategy of exploiting the
conditional independence of the programs conditioned on the DSL, and
so alternate between estimating the DSL ($\mathcal{D},\theta$) and
estimating a posterior distribution over $p$ by searching for
programs.  In practice searching for
programs is difficult, so we use the recognition model to
learn how to search efficiently.

@@

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others.}  \label{feeding}
  \end{figure}

>>>>

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
complicated by the fact that the programs are unobserved,
and so we must solve a difficult search problem to find any programs at all. To make
search tractable we learn a bottom-up \emph{recognition
  model}, written $q(\cdot )$
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs likely to explain the input/outputs. $q(\cdot )$ implements an amortized
inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model.

@@

%% We take the intuitive strategy of exploiting the
%% conditional independence of the programs conditioned on the DSL, and
%% so alternate between estimating the DSL ($\mathcal{D},\theta$) and
%% estimating a posterior distribution over $p$ by searching for
%% programs.  In practice searching for
%% programs is difficult, so we use the recognition model to
%% learn how to search efficiently.

@@

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Provides}\\ \footnotesize{inductive bias}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others.}  \label{feeding}
  \end{figure}
